---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hmsidwR - Health Metrics and the Spread of Infectious Diseases with R

<!-- badges: start -->
<!-- badges: end -->

The goal of `{hmsidwR}` is to provide the set of data used in the **Health Metrics and the Spread of Infectious Diseases
Machine Learning Applications and Spatial Modeling Analysis with R** book.

## Installation

You can install the development version of hmsidwR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Fgazzelloni/hmsidwR")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r load data}
library(hmsidwR)
library(dplyr)
data(sdi90_19)
head(subset(sdi90_19,location=="Global"))
```



```{r example1}
sdi_avg <- sdi90_19|>
  group_by(location)|>
  reframe(sdi_avg=round(mean(value),3))

head(sdi_avg)
```


```{r example2}
sdi90_19 |>
  filter(location%in%c("Global","Italy","France","Germany"))|>
  group_by(location)|>
  reframe(sdi_avg=round(mean(value),3))|>
  head()
```

